|

### 2022-12-12 r-report/Paper.Rmd
zwischenstand

```{r setup-ex}
source('r-imports/init.R')
source('r-analysis/meta.R')
```

@@

The question arises, how China plans to curb its emissions. At the United Nations General Assembly in 2020, Chinese President Xi Jinping announced the goal of Chinese carbon neutrality before 2060 [@Jinping2020]. This was the first time China officially committed to a long-term emissions reductions goal [@CAT2022]. One year later, in November 2021, ahead of COP26, China submitted its updated NDC to the UNFCCC. Accordingly, the country plans to peak its carbon emissions before 2030, decrease the carbon intensity of GDP by over 65% (relative to 2005), have around 25% of non-fossil fuels in primary energy consumption by 2030, increase the forest stock volume by six billion cubic meters until 2030 and have 1,200 GW of wind and solar power capacity installed by the same year [@China2022]. Although some of these objectives are vague to some degree, and the emissions reduction target is only a relative goal, the ambitions China has set for itself are a marked improvement over the targets set out in the previous 2016 NDC. Additionally, it is important to note that these goals are unconditional and hence not relying on external climate finance. China has adopted numerous policies to support its international targets, such as the “Working Guidance for Carbon Dioxide Peaking and Carbon Neutrality” and the “Action Plan for Carbon Dioxide Peaking Before 2030”. The former spells out a set of principles and sectoral goals to achieve carbon dioxide peaking and carbon neutrality, among them the need to exercise nationwide planning and the prioritization of conversing energy [@DRCEP2021a]. The latter defines key tasks for driving the low-carbon energy transition or saving energy, carbon emission mitigation and efficiency improvement [@DRCEP2021b]. With its “14th Five-Year Plan on Renewable Energy”, the country aims to further accelerate its renewable energy expansion. By 2025, 33% of electricity ought to be supplied by renewable sources (18% non-hydro), which could decrease annual carbon emissions by 2.6 gigatons [@Zhou2022].

@@

With these developments in mind and following up on China’s claim to be a developing country, we set out in this paper to discuss equity considerations for China, focusing on two research questions. First, we will investigate whether China, from an emissions perspective, can still be characterized as a developing nation. For this we compare China’s Kaya identity with other developing and developed nations. Furthermore, we consider China’s sectoral emissions trends and contrast them with those of (other) developing and developed nations, controlling for differences in population size and GDP. Secondly, we investigate China’s claim of developed countries’ being the driver of climate change, by calculating different measures of (historic) responsibility and assess the level of responsibility China bears in combatting climate change. We discuss these findings with regards to a projection of China’s cumulative emissions.

@@

```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
YEAR_L = 1970
YEAR_U = 2020
GAS = "GHG"

@@

```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

TO BE DONE FOrmula

@@

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|}
    \hline
        \textbf{Group  } & \textbf{Thresholds July 2019 in USD  } \\ \hline
        Low income   & $< 1,026$ \\ \hline
        Lower-middle income   & $1,026 - 3,955$ \\ \hline
        Upper-middle income  & $3,966 - 12,375$ \\ \hline
        High income  & $> 12,375$ \\ \hline
    \end{tabular}
\end{table}

@@

With a Kaya identity, one can identify the main driving forces of CO2 emissions in a certain period. The Kaya identity expresses CO2 emissions (F) as a function of GDP (G), population (P) and energy (E):

TO BE DONE FOrmula

The term highlights the different components of the identity: G/P is GDP per capita, E/G is the energy intensity of GDP and F/E is the carbon intensity of energy [@Lamb2021]. By comparing Kaya identities of different regions, we can also discuss regional differences. Hence, we use the Kaya identity to discuss if the driving forces of emissions show similarities with developing or developed nations.

@@

Comparing China’s Kaya identity to the decomposition of the development of CO2 emissions of developing and developed countries does not provide a clear result on whether China can be considered a developing or developed nation. In general, economic growth is the main driver of CO2 emissions, both in developed and developing nations. However, GDP per capita growth is much larger and hence closer to China’s figures in developing nations as they show a greater growth potential. Overall carbon emissions are decreasing in developed nations while they are increasing in developing nations and China. This supports the notion of China being a developing country relying on emissions driven growth. On the other hand, China’s energy and carbon intensity are decreasing as it is the case for developed countries. The population’s development of China also more closely resembles the trend of developed countries than those of developing countries. To sum up, this classification does not clearly indicate whether China is a developing or developed country. As mentioned above, comparing China to a more granular classification of countries might be worthwhile, as the EDGAR dataset for example considers Saudi-Arabia, a country with one of the highest GDP per capita as a developing nation.

```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 201
COUNTRY = "China"
GAS = "GHG"

@@

```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r,fig.cap="Figure 6"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 7"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

To sum up, China has a very high responsibility to mitigate climate change, even the highest responsibility of all countries when considering some of the discussed equity metrics. Based on our calculations, China is likely to surpass the EU well before 2030 and the US shortly after in 2032 in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter. The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic responsibility beyond CO2 emissions –  especially in light of growing capabilities, issue salience and data availability that all put greater responsibility recent emissions. 
Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed. 
However, we also need to consider that China only ranks on 81st and 43rd place considering their GDP per capita and their emissions per capita, respectively. This diminishes China’s responsibility to some extent, showing that the global community needs to grant space for economic development to be fair. However, this economic development should ideally be decoupled from a growth in emissions. If we look at the per capita emissions of the countries that rank first, we see that these are mostly very small and, from the perspective of absolute emissions, less important countries. Although these countries might have a high ability to pay from a per capita perspective, their overall economic power is not high. The opposite is true for China. China ranks first place in absolute emissions and GDP in 2019 with a great distance to subsequent ranks. 
Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.

# Discussion and Conclusion TBD

@@

Hence, we believe that China’s fair share is much higher than what they currently plan to do. Together with the EU-27 and the U.S., China should bear the highest responsibility for climate change mitigation. Its self-classification as a developing country is clearly politically motivated, to not give in to the demands of having to do more. At the same time, the political leadership in Beijing can present itself as a top student in the international community by effortlessly surpassing its own goals, as it is expected by different observers [@CAT2022].

@@

While aiming to be as comprehensive as possible our analysis has some limitations. First, we only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable. The problem of climate change caused by anthropogenic greenhouse gas emissions has only been known since the 1970s, and since the 1990s there has been a dedicated international process to address the problem. Against this background, an additional consideration of cumulative emissions in these time periods might be worthwhile. Second, the projection of future emissions rests on major simplification assumptions, it is likely that a more sophisticated approach such as an ARIMA-modelling would result in more robust estimates. Third, a comprehensive assessment of China’s responsibility could discuss further equity metrics such as a ranking of consumption-based emissions. However, this was not possible for us, as our data only included consumption-based data for approx. 100 countries and crucially missing the US, making a comparison less meaningful. Lastly, reducing capacity to mere GDP and GDP per capita considerations is very much simplifying the issue, as land area, access to renewable resources and intellectual property and many other factors determine a countries mitigation potential, which is very likely to differ by sector. 
With these limitations in mind, we believe none the less that our analysis has shed light on the special case of China and has shown that the under complex self-assessment does not withstand a thorough analysis. Keeping these assessments in mind will be worthwhile when assessing the responsibilities of upcoming developing nations. The case of China has shown that it is crucial to come to a mutual understanding of what constitutes responsibilities and how they can assessed on an objective basis. Especially our analysis of future cumulative emissions indicates that it will be key to frame the issue beyond CO2.

>>>>

```{r setup-ex}
source('r-imports/init.R')
source('r-analysis/meta.R')
theme_ghg = function(){ 
  theme_minimal() %+replace%
     theme(
       plot.title =element_blank(),
       plot.subtitle = element_blank()
    )
}
DIRECT_PLOTTING = F
```

@@

The question arises, how China plans to curb its emissions. At the United Nations General Assembly in 2020, Chinese President Xi Jinping announced the goal of Chinese carbon neutrality before 2060 [@Jinping2020]. This was the first time China officially committed to a long-term emissions reductions goal [@CAT2022]. One year later, in November 2021, ahead of COP26, China submitted its updated NDC to the UNFCCC. Accordingly, the country plans to peak its carbon emissions before 2030, decrease the carbon intensity of GDP by over 65% (relative to 2005), have around 25% of non-fossil fuels in primary energy consumption by 2030, increase the forest stock volume by six billion cubic meters until 2030 and have 1,200 GW of wind and solar power capacity installed by the same year [@China2021]. Although some of these objectives are vague to some degree, and the emissions reduction target is only a relative goal, the ambitions China has set for itself are a marked improvement over the targets set out in the previous 2016 NDC. Additionally, it is important to note that these goals are unconditional and hence not relying on external climate finance. China has adopted numerous policies to support its international targets, such as the “Working Guidance for Carbon Dioxide Peaking and Carbon Neutrality” and the “Action Plan for Carbon Dioxide Peaking Before 2030”. The former spells out a set of principles and sectoral goals to achieve carbon dioxide peaking and carbon neutrality, among them the need to exercise nationwide planning and the prioritization of conversing energy [@DRCEP2021a]. The latter defines key tasks for driving the low-carbon energy transition or saving energy, carbon emission mitigation and efficiency improvement [@DRCEP2021b]. With its “14th Five-Year Plan on Renewable Energy”, the country aims to further accelerate its renewable energy expansion. By 2025, 33% of electricity ought to be supplied by renewable sources (18% non-hydro), which could decrease annual carbon emissions by 2.6 gigatons [@Zhou2022].

@@

With these developments in mind and following up on China’s claim to be a developing country, we set out in this paper to discuss equity considerations for China, focusing on two research questions. First, we will investigate whether China, from an emissions perspective, can still be characterized as a developing nation. For this we compare China’s Kaya Identity with other developing and developed nations. Furthermore, we consider China’s sectoral emissions trends and contrast them with those of (other) developing and developed nations, controlling for differences in population size and GDP. Secondly, we investigate China’s claim of developed countries’ being the driver of climate change, by calculating different measures of (historic) responsibility and assess the level of responsibility China bears in combatting climate change. We discuss these findings with regards to a projection of China’s cumulative emissions.

@@

```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 1970
YEAR_U = 2020
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

$$\text{GNI} = \text{GDP} + \left (\text{EX}_{FS} - \text{IM}_{FS} \right )$$

whereas $\text{GNI}$ be the gross national income, $\text{GDP}$ be the gross domestic product, $\text{EX}_{FS}$ be the money flowing from, and $\text{IM}_{FS}$ the money flowing to foreign countries.

@@

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|}
    \hline
        \textbf{Group  } & \textbf{Thresholds July 2019 in USD  } \\ \hline
        Low income   & $< 1026$ \\ \hline
        Lower-middle income   & $1026 - 3955$ \\ \hline
        Upper-middle income  & $3966 - 12375$ \\ \hline
        High income  & $> 12375$ \\ \hline
    \end{tabular}
    \caption{Classification Thresholds\label{tbl:x}}
\end{table}

@@

With a Kaya Identity, one can identify the main driving forces of CO2 emissions in a certain period. The Kaya Identity expresses CO2 emissions $F$ as a function of GDP $G$, population $P$ and energy $E$:

$$F = P \: \frac{G}{P} \frac{E}{G} \frac{F}{E}$$

whereas $\frac{G}{P}$ represents GDP per capita, $\frac{E}{G}$ represents the energy intensity of GDP and $\frac{F}{E}$ represents the carbon intensity of energy [@Lamb2021]. By comparing Kaya identities of different regions, we can also discuss regional differences. Hence, we use the Kaya Identity to discuss if the driving forces of emissions show similarities with developing or developed nations.

@@

Comparing China’s Kaya Identity to the decomposition of the development of CO2 emissions of developing and developed countries does not provide a clear result on whether China can be considered a developing or developed nation. In general, economic growth is the main driver of CO2 emissions, both in developed and developing nations. However, GDP per capita growth is much larger and hence closer to China’s figures in developing nations as they show a greater growth potential. Overall carbon emissions are decreasing in developed nations while they are increasing in developing nations and China. This supports the notion of China being a developing country relying on emissions driven growth. On the other hand, China’s energy and carbon intensity are decreasing as it is the case for developed countries. The population’s development of China also more closely resembles the trend of developed countries than those of developing countries. To sum up, this classification does not clearly indicate whether China is a developing or developed country. As mentioned above, comparing China to a more granular classification of countries might be worthwhile, as the EDGAR dataset for example considers Saudi-Arabia, a country with one of the highest GDP per capita as a developing nation.

```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 201
COUNTRY = "China"
GAS = "GHG"

@@

```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r,fig.cap="Figure 6"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR = 1950
GAS = "GHG"
COUNTRY = "China"

source("r-analysis/data_sector_regions_yemission.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_facet_regions_sectors_yemission_stacked_rel.R", local = TRUE, print.eval = TRUE)

@@

```{r,fig.cap="Figure 7"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR = 1950
GAS = "GHG"
COUNTRY = "China"

source("r-analysis/data_sectror_incomelevel_yemissions.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_facet_incomelevels_sectors_yemission_stacked_rel.R", local = TRUE, print.eval = TRUE)

@@

To sum up, China has a very high responsibility to mitigate climate change, even the highest responsibility of all countries when considering some of the discussed equity metrics. Based on our calculations, China is likely to surpass the EU well before 2030 and the US shortly after in 2032 in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter. The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic responsibility beyond CO2 emissions –  especially in light of growing capabilities, issue salience and data availability that all put greater responsibility recent emissions.

Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed.

However, we also need to consider that China only ranks on 81st and 43rd place considering their GDP per capita and their emissions per capita, respectively. This diminishes China’s responsibility to some extent, showing that the global community needs to grant space for economic development to be fair. However, this economic development should ideally be decoupled from a growth in emissions. If we look at the per capita emissions of the countries that rank first, we see that these are mostly very small and, from the perspective of absolute emissions, less important countries. Although these countries might have a high ability to pay from a per capita perspective, their overall economic power is not high. The opposite is true for China. China ranks first place in absolute emissions and GDP in 2019 with a great distance to subsequent ranks.

Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.

# Discussion and Conclusion

@@

Hence, we believe that China’s fair share is much higher than what they currently plan to do. Together with the EU-27 and the U.S., China should bear the highest responsibility for climate change mitigation. Its self-classification as a developing country is clearly politically motivated, to not give-in to the demands of raising its ambition. At the same time, the political leadership in Beijing can present itself as a top student in the international community by effortlessly surpassing its own goals, as it is expected by different observers [@CAT2022].

@@

While aiming to be as comprehensive as possible our analysis has some limitations. First, we only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable. The problem of climate change caused by anthropogenic greenhouse gas emissions has only been known since the 1970s, and since the 1990s there has been a dedicated international process to address the problem. Against this background, an additional consideration of cumulative emissions in these time periods might be worthwhile. Second, the projection of future emissions rests on major simplification assumptions, it is likely that a more sophisticated approach such as an ARIMA-modelling would result in more robust estimates. Third, a comprehensive assessment of China’s responsibility could discuss further equity metrics such as a ranking of consumption-based emissions. However, this was not possible for us, as our data only included consumption-based data for approx. 100 countries and crucially missing the US, making a comparison less meaningful. Lastly, reducing capacity to mere GDP and GDP per capita considerations is very much simplifying the issue, as land area, access to renewable resources and intellectual property and many other factors determine a countries mitigation potential, which is very likely to differ by sector.

With these limitations in mind, we believe none the less that our analysis has shed light on the special case of China and has shown that the under complex self-assessment does not withstand a thorough analysis. Keeping these assessments in mind will be worthwhile when assessing the responsibilities of upcoming developing nations. The case of China has shown that it is crucial to come to a mutual understanding of what constitutes responsibilities and how they can assessed on an objective basis. Especially our analysis of future cumulative emissions indicates that it will be key to frame the issue beyond CO2.
